Impact of Education on Entrepreneurship - Data Gathering and Analysis

### 2014-11-21 GEMDataSource.Rmd
New data for equations

@@

# Create regression output table
labels <- c('Percent Perceived', 'Percent Fear',
            'Annual GDP Growth', 'Percent Opportunities', 'Percent Fear x Percent Opportunities','(Intercept)')

stargazer::stargazer(R1, R2, R3, covariate.labels = labels, 
                     title = 'Linear Regression Estimates', digits = 2, type = 'html')
```
<br>

@@

>>>>

1. $PercentIntention = PercentPerceived(Perceived Capabilities) + GEM D01 way of teaching + PercentOpportunities(Perceived Opportunities)$

@@

# Create regression output table
labels <- c('National Level Avg Perceived Capabilities', 'National Level Avg Fear of Failure',
            'Annual GDP Growth', 'National Level Avg Perceived Good Opportunities', 'National Level Avg Fear of Failure x National Level Avg Perceived Good Opportunities','(Intercept)')

dlables <- c('National Level Average Percent Entrepreneurial Intention', 'National Level Nascent Entrepreneural Activity', 'National Level Average Percent Owning a Business')

stargazer::stargazer(R1, R2, R3, covariate.labels = labels, dep.var.labels = dlables,
                     title = 'Linear Regression Estimates', digits = 2, type = 'html')
```
<br>  
National-level average of people perceiving opportunities but acknowledging fear of failure will prevent them from creating a business (FF)

@@

```{r echo = FALSE, cache=TRUE, include=TRUE, results='asis', warning=FALSE}
library(xtable)
Table1 <- xtable(summary(CompleteDataset))
xtable(CompleteDataset, type = 'html')

library(stargazer)
stargazer(CompleteDataset, column.sep.width = "20pt", type = 'html')
